Synthesising Recursive Functions for First-Order Model Counting:\\ Challenges, Progress, and Conjectures

### 2023-03-08 doc/paper/paper.tex
An experiment

% TODO (at the very end)
% grammarly the whole thing (supplementary material as well)
% make sure the result table (as well as other floating objects) are on the right pages
% make sure the abstract, introduction, and conclusion are all in line with each other
% maybe improve the indentation of equations

@@

\newcommand{\crefrangeconjunction}{--}
\newcommand\pfun{\mathrel{\ooalign{\hfil$\mapstochar\mkern5mu$\hfil\cr$\to$\cr}}}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\FOtwo}{$\mathsf{FO}^{2}$}
\newcommand{\FOthree}{$\mathsf{FO}^{3}$}
\newcommand{\SFO}{$\mathsf{S}^{2}\mathsf{FO}^{2}$}
\newcommand{\SRU}{$\mathsf{S}^{2}\mathsf{RU}$}
\newcommand{\Uone}{$\mathsf{U}_{1}$}
\newcommand{\Ctwo}{$\mathsf{C}^{2}$}
\newcommand{\IFO}{$\mathsf{I}\mathsf{FO}^{2}$}
\newcommand\mdoubleplus{\mathbin{+\mkern-10mu+}}
\newcommand{\Done}{\domainNames_{1}}
\newcommand{\Dtwo}{\domainNames_{2}}
\newcommand{\Dthree}{\domainNames_{3}}
\newcommand{\predicate}{\texttt{\textup{p}}}
\newcommand{\predicateq}{\texttt{\textup{q}}}
\newcommand{\nulll}{\texttt{\textup{null}}}

@@

% TODO: I think I said this the last time, but along with the complexities as a
% way of representing the empirical evaluation, I think you should also include
% a few plots, even if they say nothing more than what the table already says.
% The point is that the readers can see what this behaviour looks like so even
% if you include a few plots and say we just give a few representative examples
% and the rest follow the table of all that will be better [an experiment with
% non-partial endo injections?]

@@

>>>>

% TODO (at the very end)
% grammarly the whole thing (supplementary material as well)
% make sure the result table (as well as other floating objects) are on the right pages
% reread the entire paper

@@

\newcommand{\crefrangeconjunction}{--}
\newcommand\pfun{\mathrel{\ooalign{\hfil$\mapstochar\mkern5mu$\hfil\cr$\to$\cr}}}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\FOtwo}{$\mathsf{FO}^{2}$}
\newcommand{\FOthree}{$\mathsf{FO}^{3}$}
\newcommand{\SFO}{$\mathsf{S}^{2}\mathsf{FO}^{2}$}
\newcommand{\SRU}{$\mathsf{S}^{2}\mathsf{RU}$}
\newcommand{\Uone}{$\mathsf{U}_{1}$}
\newcommand{\Ctwo}{$\mathsf{C}^{2}$}
\newcommand{\IFO}{$\mathsf{I}\mathsf{FO}^{2}$}
\newcommand\mdoubleplus{\mathbin{+\mkern-10mu+}}
\newcommand{\Done}{\domainNames_{1}}
\newcommand{\Dtwo}{\domainNames_{2}}
\newcommand{\Dthree}{\domainNames_{3}}
\newcommand{\predicate}{\texttt{\textup{p}}}
\newcommand{\predicateq}{\texttt{\textup{q}}}
\newcommand{\predicates}{\texttt{\textup{s}}}
\newcommand{\predicater}{\texttt{\textup{r}}}
\newcommand{\nulll}{\texttt{\textup{null}}}

@@

@@

\subsubsection{A Comparison with \textsc{\normalfont FastWFOMC}}

\begin{figure}[t]
  \includegraphics{plot}
  \caption{The runtime data of \textsc{FastWFOMC} on the problem of counting
    permutations together with a quartic regression model fitted on all of the
    data and a linear model fitted on the first half of the data points.}
\end{figure}

\begin{itemize}
  \item permutations of a set (i.e., bijective/injective endofunctions)
  \item an extension of \textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21} with
        cardinality constraints as described by
        Ku\v{z}elka~\shortcite{DBLP:journals/jair/Kuzelka21}, provided by one of
        the authors of \textsc{FastWFOMC}.
  \item can be described in \FOtwo{} with cardinality constraints as
  \begin{align*}
    &(|\predicate| = |\Delta|) \land{}\\
    &(\forall X, Y \in \Delta\text{. } \predicater(X) \lor \neg \predicate(X, Y)) \land{}\\
    &(\forall X, Y \in \Delta\text{. } \predicates(X) \lor \neg\predicate(Y, X)),
  \end{align*}
        where $\predicater$ and $\predicates$ are Skolem predicates as described
        by Van den Broeck et al.~\shortcite{DBLP:conf/kr/BroeckMD14}, and
        $|\Delta|$ ranges from 1 to 50.
  \item \textsc{FastWFOMC} was run on an AMD Ryzen~7~5800H processor with
        \SI{16}{\giga\byte} of memory, running Arch Linux~6.2.2-arch1-1 and
        Python~3.10.9.
  \item degrees 4--7 are about equally well-fitting (maybe include the fit
        numbers?)
\end{itemize}
